\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\large\scshape}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2\\
\textit{\small #3} & \textit{\small #4}
\end{tabular*}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2
\end{tabular*}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\begin{center}
{\Huge \textbf{ANANTHU A}}\\
\vspace{3pt}
+91 9188265915 $|$
\href{mailto:ananthuanilkumar82@gmail.com}{ananthuanilkumar82@gmail.com} $|$
\href{https://github.com/anndua}{github.com/anndua} $|$
\href{https://www.linkedin.com/in/ananthu-anilkumar-789726405/}{LinkedIn}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Model Engineering College}{Thrikkakara, Kerala}
{B.Tech in Computer Science and Business Systems}{Expected Graduation: 2028}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{API Observe -- FastAPI, PostgreSQL, SQLModel, Docker, JWT}{}
\resumeItemListStart
\resumeItem{Built a backend API observability platform to collect and analyze API request metrics.}
\resumeItem{Designed REST APIs using FastAPI and SQLModel with PostgreSQL.}
\resumeItem{Implemented JWT authentication, API key validation and request tracking.}
\resumeItem{Containerized the application using Docker.}
\resumeItem{GitHub: \href{https://github.com/anndua/api-observe}{github.com/anndua/api-observe}}
\resumeItemListEnd

\resumeProjectHeading{Calorie Tracker -- FastAPI, PostgreSQL, Docker, JWT}{}
\resumeItemListStart
\resumeItem{Developed a REST API for calorie and meal tracking.}
\resumeItem{Integrated external nutrition APIs for food information.}
\resumeItem{Implemented JWT authentication and protected endpoints.}
\resumeItem{Containerized the backend using Docker.}
\resumeItem{GitHub: \href{https://github.com/anndua/calorie-tracker}{github.com/anndua/calorie-tracker}}
\resumeItemListEnd

\resumeProjectHeading{Personal Finance Advisor -- FastAPI}{}
\resumeItemListStart
\resumeItem{Developed backend APIs for a team-based personal finance application.}
\resumeItem{Implemented authentication and financial management endpoints.}
\resumeItem{Collaborated using Git and REST API design practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in,label={}]
\item \small{
\textbf{Languages:} Python, SQL, C, C++\\
\textbf{Backend:} FastAPI, REST APIs, SQLModel, SQLAlchemy, JWT Authentication\\
\textbf{Databases:} PostgreSQL, Redis\\
\textbf{Developer Tools:} Docker, Git, GitHub, Linux, VS Code, Alembic
}
\end{itemize}

\section{Relevant Coursework}
\begin{itemize}
\item Data Structures and Algorithms
\item Database Management Systems
\item Operating Systems
\item Computer Networks
\item Object-Oriented Programming
\end{itemize}

\end{document}
